EDA

### 2020-03-01 src/EDA&mode_fitting.Rmd
Cor Plot

## Correlation for continuous variables
rate_class <- pct_final %>% ggplot(aes(x=assessTotal_pct,y=rate_pct,group=Municipalities,color=Municipalities)) + geom_point() + ggtitle("mill rate and tax") + geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")

assess_class <- pct_final %>% ggplot(aes(x=tax,y=rate_pct,group=Municipalities,color=Municipalities)) + geom_point() + ggtitle("assessTotal for taxClass 1 and all municipalities") + geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")

rate_class

@@

## Correlation for categorical variables
TaxClassCode <- aov(rate_pct ~ TaxClassCode, data = pct_final)
summary(TaxClassCode)

@@

Municipalities <- aov(rate_pct ~ Municipalities, data = pct_final)
summary(Municipalities)

TaxClassCode <- aov(rate_pct ~ TaxClassCode, data = pct_final)
summary(TaxClassCode)
```

@@

>>>>

## Correlation for continuous variables
assess_class <- assessment_aggregate %>% ggplot(aes(x=assessTotal,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_point() + ggtitle("mill rate and assess - cor") + geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")

tax_class <- assessment_aggregate %>% ggplot(aes(x=predTaxIncome,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_point() + ggtitle("mill rate and tax - cor") + geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")

@@

tax_class

## Correlation for categorical variables
TaxClassCode <- aov(rate ~ TaxClassCode, data = assessment_aggregate)
summary(TaxClassCode)

@@

Municipalities <- aov(rate ~ AddressAssessorMunicipalityDesc, data = assessment_aggregate)
summary(Municipalities)
```

@@

# linear1<-lm(rate~factor(Year)+factor(TaxClassCode)+factor(AddressAssessorMunicipalityDesc)+assessTotal+predTaxIncome,data=assessment_aggregate)
# summary(linear1)

linear<-lm(rate~.,data=assessment_aggregate)
summary(linear)
